---
title: "Asset Data Cleaning"
author: "Ibrahim Khan & Luke Sonnet"
output: md_document
editor_options: 
  chunk_output_type: console
---


```{r}
library(tidyverse)
cleaned_assets <- read_csv("analysis/data_cleaning/01_assets.csv")

# rely on key as unique id
if (any(duplicated(cleaned_assets$key))) {
  stop("Some duplicated keys!")
}
```

### Part 2: Cleaning the Asset form variables.

This includes all variables measuring immovable, movable property and business capital as reported in the asset form. The data in the affidavit will be dealt with in a separate section. 


#### Immovable property inside Pakistan

```{r}
#table(cleaned_assets$im_prop_pak_g_count)
#cleaned_assets <- haven::read_dta("data/rsols_data/Luke_08282018_Asset.dta")
table(cleaned_assets$im_prop_pak, cleaned_assets$entry, useNA = "a")
cleaned_assets %>%
  select(starts_with("im_prop_pak")) %>%
  summarize_all(funs(nas = sum(is.na(.))))

with(cleaned_assets, table(is.na(im_prop_pak_p_1), im_prop_pak))
with(cleaned_assets, table(im_prop_pak, entry, useNA = "always"))
tail(with(cleaned_assets, table(im_prop_pak_p_1, entry, useNA = "always")))

with(filter(cleaned_assets, im_prop_pak == 0), table(im_prop_pak_p_1, useNA = "a"))

with(cleaned_assets, table(im_prop_pak > 0 & !is.na(im_prop_pak), im_prop_pak_p_1 > 0 & !is.na(im_prop_pak_p_1)))

# Property and business prices
prop_capital_long <- cleaned_assets %>%
  select(key, im_prop_pak, im_prop_pako, bus_cap_wpk_count, bus_cap_opk_count,
         starts_with("im_prop_pak_p"), starts_with("im_prop_pako_p"),
         starts_with("bus_cap_wpk_am"), starts_with("bus_cap_opk_am")) %>%
  gather(var, val, -key) %>%
  mutate(val = as.numeric(val),
         val = ifelse(val < 0, NA, val))

m_prop_capital_wide <- prop_capital_long %>%
  spread(var, val)

m_prop_capital_totals <- prop_capital_long %>%
  mutate(var = gsub("_[0-9]+$", "", var)) %>%
  group_by(key, var) %>%
  summarize(total = sum(val, na.rm = TRUE)) %>%
  filter(var %in% c("im_prop_pako_p", "im_prop_pak_p", "bus_cap_wpk_am", "bus_cap_opk_am")) %>%
  mutate(var = paste0(var, "_total")) %>%
  spread(var, total)
#A. converting negatives to missing values
m_prop_types <- cleaned_assets %>%
  select(key, 
         starts_with("im_prop_pak_t"), starts_with("im_prop_pako_t")) %>%
  mutate_at(
    vars(starts_with("im_prop_pak_t"), starts_with("im_prop_pako_t")),
    funs(recode(
      .,
      `1` = "Residential",
      `2` = "Agricultural",
      `3` = "Commercial",
      `777` = "Other",
      .default = NA_character_
    ))
  ) %>%
  mutate_at(
    vars(starts_with("im_prop_pak_a"), starts_with("im_prop_pako_a")),
    funs(recode(
      .,
      `1` = "Rural",
      `2` = "Urban",
      .default = NA_character_
    ))
  )

# TODO clean names?
bus_names <- cleaned_assets %>%
  select(key, starts_with("bus_cap_wpk_na"), starts_with("bus_cap_opk_na")) %>%
  gather(var, val, -key)

# the variables im_prop_pak_t and im_prop_pak_a are of LABELLED type, hence letting them stay as is. 

# cleaned_assets%>%
#   mutate(correct_sum=im_prop_pak_totes==im_prop_pak_agg)%>%
#   select(im_prop_pak_p_1,im_prop_pak_p_2,im_prop_pak_p_3,im_prop_pak_p_4, im_prop_pak_agg, im_prop_pak_totes,correct_sum)

# So, clearly, the previous aggregate was incorrect and this new one is correct. One prob: all those with all NAs, their sum is given as 0, not NA.

```
**IMP**: The new variable that measures the total of values of all immovable property in Pakistan is **im_prop_pak_totes**. One issue with this variable is that the sums of all NAs is also declared as 0 and not NA. 

#### Other Asset Measures - Bank Drafts: Motor_cost and Investments Total

```{r}
# table(cleaned_assets$bank_drafts)
# table(cleaned_assets$machinery)
# table(cleaned_assets$other_remitted, useNA = "always")

m_other_capital <- cleaned_assets %>%
  select(key, inest_icp, starts_with("invest_"), bank_drafts, machinery, other_remitted,
         assest_remit) %>%
  rename(invest_icp = inest_icp) %>%
  mutate_at(vars(starts_with("invest_"), bank_drafts, machinery, other_remitted, assest_remit),
            funs(ifelse(. < 0 | . == 99, NA, .)))
table(cleaned_assets$assest_remit)

m_invest_totals <- m_other_capital %>%
  select(key, starts_with("invest")) %>%
  gather(var, val, -key) %>%
  group_by(key)%>%
  summarize(invest_total = sum(val, na.rm = TRUE))

m_motor_cost <- cleaned_assets %>%
  mutate(motor_value = ifelse(motor_cost < 1, NA, motor_cost)) %>%
  select(key, motor_value)


cars <- read_csv("data/rsols_corrections/car_data.csv")
m_car_totals <- cars %>%
  select(key, `Motor Number`) %>%
  rename(motor_number = `Motor Number`) %>%
  filter(!is.na(motor_number))
m_car_totals

intersect(m_car_totals$key, m_motor_cost$key[!is.na(m_motor_cost$motor_value)])
# TODO: model for car value
```
**IMP**: The new variable **invest_totes** sums up all investments types.


#### Jewellery

```{r}
str(cleaned_assets$jewel_cost)
str(cleaned_assets$jewel_tolas)

m_jewelry <- cleaned_assets %>%
  mutate_at(
    vars(jewel_cost, jewel_tolas),
    funs(ifelse(. < 0, NA, .))
  ) %>%
  mutate_at(
    vars(jewel_cost, jewel_tolas),
    funs(
      case = case_when(
        . > 0 ~ "Positive",
        . == 0 ~ "Zero",
        is.na(.) ~ "Not Available"
      )
    )
  ) %>%
  select(key, jewel_cost, jewel_tolas)
m_jewelry
#with(m_jewelry, table(jewel_cost_case, jewel_tolas_case))
# TODO impute jewelry value
```


#### Other Assets, Savings and Liabilites

```{r}
m_cash_liabilities <- cleaned_assets %>%
  mutate_at(
    vars(
      cash_cost, cash_bank_cost, aopu_cost, attp_cost,
      other_assests_cost, liabilities
    ),
    funs(ifelse( . < 0, NA, .))
  ) %>%
  rename(cash = cash_cost,
         cash_bank = cash_bank_cost,
         furniture_value = aopu_cost,
         assets_transferred_to_others_value = attp_cost,
         other_assets_value = other_assests_cost) %>%
  select(key, cash, cash_bank, furniture_value, assets_transferred_to_others_value,
         other_assets_value, liabilities)

m_cash_liabilities
```

### Part 3: Cleaning the Affidavit variables.


#### Candidate General Info

```{r}
registration <- cleaned_assets %>%
  rename(
    registered_sr_no = sr_no,
    registered_electoral_area = electoral_area,
    registered_tehsil = tehsil,
    registered_district = district
  ) %>%
  select(starts_with("registered_"))
# table(m_registration$registered_sr_no)
# unique(m_registration$registered_electoral_area)
# unique(m_registration$registered_tehsil)
# cand_vote_district=ifelse(dist_has_only_nums, NA, cand_vote_district),
#          cand_vote_district=recode(cand_vote_district, 
#                                    `Sanghar3` ="Sanghar",
#                                    `Korangi`= "Korangi", 
#                                    `Eas5` = "East"),
#          cand_vote_tehsil=ifelse(tehsil_has_only_nums | cand_vote_tehsil %in% c("-O9","_99"), NA, cand_vote_tehsil),
#          cand_vote_tehsil=recode(cand_vote_tehsil,
#                                  `Cit6 Lahore`="Lahore",
#                                  `Lh4` = "Lahore")

#renaming so aren't confused with the tehsil district of the place where elections are being contested. 

# table(cleaned_assets$cand_vote_electoral_area)
#this is varied. Has weird numbers or text. How to fix this?

# will/can clean district and tehsil vars

# district
# table(cleaned_assets$cand_vote_district)
filter(cleaned_assets, constituency_code == "NA-253") %>%
  select(candidate_name, dependents)

educ_none <- c(
  "no", "nil", "nill","ni","n,a","No", "No education", 
  "No formal education", "No Formal Education","No Faormal Education", "Nill",
  "Nilk","Nil","Na","N.A","N,e.d","N,A","Illtrate","Illitrate","Illiterate",
  "Illetrate","Illeterate","Illatreat","Iletrate","ILLitrate","-NiZ","0",
  "_99", "-99", "99", "o", "uneducated", "-9", "-9999", "under primary", "a",
  "-999", "un educated", "unedu", "uneducation", "none", "niil"
)
educ_primary <- c(
  "5th", "primary", "5", "7th", "litrate", "literate", "primery", "under middle", "litterate",
  "5 th", "5 pas", "basic education"
)
educ_middle <- c(
  "middle", "under matric", "middel", "8", "8th", "middle pass", "non matric",
  "9th", "midle", "undr matric", "8th class", "9", "under metric", "meddle", "mifdle", "midlle"
)
# Same as finishing 10th grade, secondary completion
educ_matric <- c(
  "matric", "matriculation", "ssc", "metric", "mtric", "o level", "10th", 
  "mattic", "o levels", "high school diploma", "mateic", "matirc", "matrik",
  "matroc", "mayric", "d com", "dhms", "icom", "diploma", "dcom", "i com", "graguate"
)
# vocational equivalent to 12th grade
educ_dae <- c("dae")
# 11th and 12th grade, pre-college finals, some more specialization
educ_intermediate <- c(
  "fa", "intermediate", "inter", "intermidiate", "fsc", "f a", "a level", "hsc",
  "a levels", "intermediat", "hssc", "inter medeat",
  "itermediate", "post graduate", "fac"
)
educ_voc_bachelors <- c("b tech", "b", "be", "be electronics", "b e", "btech", "bed", "engineering", "engineer", "civil engineer", "bit", "electrical engineering")
educ_bachelors <- c(
  "ba", "bsc", "bcom", "bba", "b com", "b a", "bs", "ballb", "bachelor",
  "bds", "bsc hons", "ba bed", "bcs", "be civil", "bachelor of arts", "ba b ed",
  "bacholar", "b sc", "bs hons", "bachelor of commerce", "bachlor", 
  "bsc engineering", "bscs", "ba in arts", "bachelor's", "bachelors", "bba finance",
  "becholar", "m bbs", "m bbs", "mbs"
)
educ_llb <- c(
  "llb", "ba llb", "law graduate",  "llm", "ba llb", "ba  llb", "bcom llb",
  "ba/llb", "llb hons", "bar at law", "bsc llb", "law", "b a llb",
  "barrister at law", "b a l l b", "b com llb", "llb ba", "ba bed llb",
  "be llb", "l lb", "ll b"
)
educ_masters <- c(
  "ms", "ma", "mba", "mbbs", "msc", "masters", "master", "ma political science",
  "mphil", "mcom", "m phil", "ma english", "mba llb", "ma llb", "m a",
  "ma islamiyat", "mallb", "ma bed", "mphill", "ma economics", "msc llb",
  "ma pol science", "ma urdu", "ma islamiat", "ma phill", "ma education", 
  "ma history", "med", "double ma", "ma islamyat", "master in ir", 
  "msc chemistry", "msc physics", "llb ma", "m a political science", "mcs",
  "mpa llb", "m phill", "m com"
)
educ_phd <- c("phd", "md")
educ_dars <- c("dars e nizami", "darse nizami", "darse nazami")
educ_relig <- c("islami", "islamic education")
# education?

cleaned_assets %>%
  mutate(educ = gsub("\\.|\\,", "", tolower(educ))) %>%

  filter(!(educ %in% c(
    tolower(educ_none), educ_bachelors, educ_dae, educ_dars, educ_intermediate,
    educ_llb, educ_masters, educ_matric, educ_middle, educ_none, educ_phd,
    educ_primary, educ_voc_bachelors
  ))) %>%
  head(100) %>%
  as.data.frame

m_demographics <- cleaned_assets %>%
  mutate_at(
    vars(educ, occup), 
    funs(
      ifelse(
        . %in% c("","- 99", "-9","-99","-999","-9999","-9o","-o9","=99",
                 "?nn", "--99","--99","_99","-98","-990","-9o9","199",
                  "99","=99"),
        NA,
        .
      )
    )
  ) %>%
  rename(num_spouse_dependents = dependents) %>%
  select(key, num_spouse_dependents, educ) %>%
  mutate(
    num_spouse_dependents = ifelse(
      num_spouse_dependents < 0 | num_spouse_dependents > 100,
      NA,
      num_spouse_dependents
    ),
    educ = gsub("\\.|\\,", "", tolower(educ)),
    educ = case_when(
      educ %in% gsub("\\.|\\,", "", tolower(educ_none)) ~ "None",
      educ %in% educ_bachelors ~ "Bachelors",
      educ %in% educ_dae ~ "Vocational Matriculation",
      educ %in% educ_dars ~ "Religious (Dars E Nizami)",
      educ %in% educ_intermediate ~ "Intermediate",
      educ %in% educ_llb ~ "LLB/LLM",
      educ %in% educ_masters ~ "Masters",
      educ %in% educ_matric ~ "Matriculation",
      educ %in% educ_middle ~ "Middle",
      educ %in% educ_phd ~ "Doctorate",
      educ %in% educ_primary ~ "Primary",
      educ %in% educ_voc_bachelors ~ "Vocational Bachelors",
      educ %in% educ_relig ~ "Religious (other)",
      substr(educ, 1, 3) %in% c("ma ", "m a", "ma/", "mab", "mba", "msc", "ms ") ~ "Masters",
      grepl("llb", educ) ~ "LLB/LLM",
      grepl("llm", educ) ~ "LLB/LLM",
      substr(educ, 1, 3) %in% c("ba ", "bs ", "b a", "bac", "bcs", "bbm", "bc0", "bco") ~ "Bachelors",
      substr(educ, 1, 3) %in% c("be ", "b e", "b t") ~ "Vocational Bachelors",
      substr(educ, 1, 4) %in% c("bsc ", "mbbs", "bech") ~ "Bachelors",
      grepl("bachelor|bachlor|bachalar|bachel|bacholar|batch|beachu|bavhelor", educ) ~ "Bachelors",
      grepl("bachlor", educ) ~ "Bachelors",
      grepl("phd", educ) ~ "Doctorate",
      !grepl("under", educ) & (grepl("9", educ) | grepl("middle", educ)) ~ "Middle",
      !grepl("under", educ) & grepl("5|6|7|educated|six|seven|priamry", educ) ~ "Primary",
      !grepl("under", educ) & grepl("4", educ) ~ "Below Primary",
      !grepl("under", educ) & grepl("matric|second", educ) ~ "Matriculation",
      grepl("n[ia]zami", educ) ~ "Religious (Dars E Nizami)",
      substr(educ, 1, 3) == "ass" | grepl("associat", educ) ~ "Vocational Matriculation",
      grepl("dae", educ) ~ "Vocational Matriculation",
      grepl("master", educ) ~ "Masters",
      substr(educ, 1, 4) == "matr" ~ "Matriculation",
      substr(educ, 1, 4) %in% c("grau", "grad", "intw", "inte", "inye") ~ "Intermediate",
      grepl("law|barister|barrist|advoc|ll.b|lzlb|l l b", educ) ~ "LLB/LLM",
      grepl("under m[at]|under\\s*gr", educ) ~ "Middle",
      grepl("bsc|bba", educ) ~ "Bachelors",
      grepl("2|3|under parim", educ) ~ "Below Primary",
      grepl("8|milddle|mddle", educ) ~ "Middle",
      grepl("a.*level|american high school|high[er]* secondary|atric|under fa|metric|maric|martic|matiix|marric|matticulation|mtaric|mwtric", educ) ~ "Matriculation",
      grepl("o.*level|10|secondary|ics|post graduation|enter|imtermediate|inatermediat|intr|hsc intermediate", educ) ~ "Intermediate",
      grepl("p hd", educ) ~ "Doctorate",
      grepl("prim|non graduate", educ) ~ "Primary",
      grepl("madra|shah[ad]|ulmaa|molvi|aalim|alam|alim|alem|hafiz|religious|aalm|faz[ai]l|khaw|tajvee|shadat|islami|allim|alma|almia|ama|almiya|quran|relig|tan[zs]eem|mufti|mov.*i", educ) ~ "Religious (other)",
      grepl("btec", educ) ~ "Vocational Bachelors",
      grepl("account|acca", educ) ~ "Vocational Bachelors",
      grepl("ms|mpa|dvm|vet|mphil|mfil|mastrs|maters|m b a|m b b s|m fil|m phil|matsers|mpjil|mph|m s c|m sc|mac", educ) ~ "Masters",
      grepl("bs|com|pharm|mbb s|mmb|b ba|b-a", educ) ~ "Bachelors",
      substr(educ, 1, 3) %in% c("dar", "der") ~ "Religious (Dars E Nizami)",
      substr(educ, 1, 3) %in% c("dip", "dba") ~ "Vocational Matriculation",
      substr(educ, 1, 6) %in% c("doctor") ~ "Doctorate",
      substr(educ, 1, 3) %in% c("fa ", "fss", "fsc", "mtr", "faa", "fca", "fs") ~ "Matriculation",
      grepl("mid|moddle", educ) ~ "Middle",
      grepl("tec|bae", educ) ~ "Vocational Bachelors",
      TRUE ~ "Other"
    ),
    educ_group = case_when(
      grepl("Vocational", educ) ~ "Vocational",
      grepl("Religious", educ) ~ "Religious",
      educ == "Below Primary" ~ "None",
      TRUE ~ educ
    )
  )

table(m_demographics$educ_group)
m_demographics %>%
  group_by(educ) %>%
  summarize(n = n()) %>%
  arrange(-n) %>% 
  head(1000) %>%
  as.data.frame

names(m_demographics)
# Occupation
# 
# mutate(
#     educ=ifelse(educ %in% ,"None",educ),
#     occup=ifelse(occup %in% c("JOBLESS","Job less","Jobless","Jobles","Jonless","N,A","N.A","N.a","N/A","NON","Na","O","O0","Un employed","Un employment","Unemploye","Unemployed","Unemployee"),"Unemployed",occup)
#   )
#     
#       NA, cand_dependents_no)

# table(cleaned_assets$cand_dependents_no, useNA = "always")
```
**IMP**: Renaming done here to allow for clarification when using variables, the prefix "cand_vote_" indicates that the details are of the place where the candidate is registered. Some cleaning of the district, tehsil and dependents number variables done. 


#### Crimes
```{r}

m_crimes <- cleaned_assets %>%
  select(key, num_criminal, starts_with("title_criminal_"), starts_with("name_court")) %>%
  mutate(num_criminal = ifelse(num_criminal < 0, NA, num_criminal)) %>%
  mutate_at(
    vars(starts_with("title_criminal_"), starts_with("name_court")),
    funs(
      ifelse( . %in% c(
          "",",","-9","-99","-9999","99","_99","Z","O","0","Nil","Nill",
          "No","N-A","Na","N/A",".","z","N","94","N.A","nil"
        ),
        NA,
        .
      )
    )
  ) %>%
  rename(crime_num = num_criminal) %>%
  select(key, crime_num)

# crimes_long <- m_crimes %>%
#   gather(var, val, -crime_num, -key) %>%
#   mutate(crime = str_extract(var, "[0-9]+"),
#          var = gsub("\\_[0-9]+", "", var)) %>%
#   spread(var, val) %>%
#   rename(crime_title = title_criminal,
#          crime_court_name = name_court,
#          crime_num = num_criminal)

```
Just some basic cleaning, removed the variable crimes_count because it was an unclean duplicate of num_criminal.

#### Income and Taxes Paid

```{r}
# str(cleaned_assets$year_income)

m_income_taxes_trips <- cleaned_assets %>%
  mutate_at(
    vars(starts_with("income_total"), starts_with("tax_paid"), intern_trips_no, intern_trips_cost), 
    funs(ifelse(. < 0, NA, .))
  ) %>%
  mutate_at(
    vars(starts_with("source_income")),
    funs(ifelse( . == "-99", NA , .))
  ) %>%
  rename(
    income_total_2017 = income_total,
    income_total_2016 = income_total2,
    income_total_2015 = income_total3,
    tax_paid_2017 = tax_paid,
    tax_paid_2016 = tax_paid2,
    tax_paid_2015 = tax_paid3,
    source_income_2017 = source_income,
    source_income_2016 = source_income2,
    source_income_2015 = source_income3,
    intern_trips_num = intern_trips_no
  ) %>%
  select(key, starts_with("source_income"), starts_with("income_total"),
         starts_with("tax_paid"), starts_with("intern_trips"))
cleaned_assets$year_income
table(m_income_taxes_trips$source_income_2015)
hist(log(m_income_taxes_trips$income_total_2017+1))
table(m_income_taxes_trips$intern_trips_num)
filter(m_income_taxes_trips, intern_trips_num == 45)
head(m_income_taxes_trips)
```
The variables year_income*'s are only binary variables and don't really give us any information when compared with the form, I suggest we delete these? 
Otherwise cleaned variables and renamed them to make them more descriptive. Newvars are titled: income_total_201*, tax_paid_20*, source_income_20*. * = {15,16,17}


#### Agricultural Income and Tax

This is similar to the income case otherwise, as the variables are already fairly clean. As in the case of year_income*'s, the variables year_agri_income*'s are also binary and don't really have any useful info for us.

```{r}
m_agriculture <- cleaned_assets %>%
  mutate_at(
    vars(
      starts_with("agri_land_holding"),
      starts_with("agri_income"), 
      starts_with("agri_income_tax")
    ), 
    funs(ifelse(. < 0, NA, .))
  ) %>%
  rename(
    agri_land_holding_2017 = agri_land_holding,
    agri_land_holding_2016 = agri_land_holding1,
    agri_land_holding_2015 = agri_land_holding2,
    agri_unit_2017 = unit_agri,
    agri_unit_2016 = unit_agri1,
    agri_unit_2015 = unit_agri2,
    agri_income_2017 = agri_income,
    agri_income_2016 = agri_income1,
    agri_income_2015 = agri_income2,
    agri_income_tax_2017 = agri_income_tax,
    agri_income_tax_2016 = agri_income_tax1,
    agri_income_tax_2015 = agri_income_tax2
  ) %>%
  select(key, starts_with("agri_"))

agri_long <- m_agriculture %>%
  gather(var, val, -key) %>%
  mutate(year = str_extract(var, "[0-9]+"),
         var = gsub("\\_[0-9]+", "", var)) %>%
  spread(var, val)
  
```

What **is** an important exercise, is converting the agricultural land holding to a single unit (I will use square feet) to allow for adequate comparison, even if we don't assign a value price for it.

Land Conversion Rates:

* 1 Marla: 225 sq feet for housing
* 1 Marla: 272.25 sq feet for agriculture (*)
* 1 Kanal = 20 Marla
* 1 Kila = 1 Acre = 8 Kanal = 8*20 = 160 Marlas
* 1 Acre = 8 Kanal = 8*20 = 160 Marlas
* I Muraba = 25 Acre = 400 Kanal = 8000 Marlas

Historically, Kilas and Acres are slightly different (+-1 kanal) but those measurements are only applicable in a few areas of South Punjab, but are now used interchangeably.


```{r}
# agri unit labels:
# 1=Muraba
# 2=Acre
# 3=Kila
# 4=Kanal
# 5=Marla

# cleaned_assets%>%
#   mutate_at(vars(starts_with("agri_land_holding_")), funs(
#     sqfeet = case_when(
#       unit_agri_2017==5 ~ 272.25*.,
#       unit_agri_2017==4 ~ 272.25*20*.,
#       unit_agri_2017==3 ~ 272.25*20*8*.,
#       unit_agri_2017==2 ~ 272.25*20*8*.,
#       unit_agri_2017==1 ~ 272.25*20*8*25*.,
#     )
#   )
#   )
# 

m_agri_total <- agri_long %>%
  mutate(
    agri_land_holding_sqfeet = case_when(
      agri_unit == 5 ~ 272.25*agri_land_holding,
      agri_unit == 4 ~ 272.25*20*agri_land_holding,
      agri_unit == 3 ~ 272.25*20*8*agri_land_holding,
      agri_unit == 2 ~ 272.25*20*8*agri_land_holding,
      agri_unit == 1 ~ 272.25*20*8*25*agri_land_holding
    )
  ) %>%
  select(key, year, agri_land_holding_sqfeet) %>%
  mutate(year = paste0("agri_land_holding_sqfeet_", year)) %>%
  spread(year, agri_land_holding_sqfeet)

#table(cleaned_assets$agri_land_holding_2017)
```
So the variables **agri_land_holding_20*_sqfeet** give us the land holdings in unit measurement (sq-feet). Next step would be to somehow find land value of these. This would be easier if we had an idea *where* the land was located, but we don't so we will have to assume a value for **average_agri_land_price per sqfeet** and then multiply by this to get a value for the land owned, but since that's just a linear increase, just using the existing ones as a measure of value is okay too, I think.


#### Cand election history, party contribution, foreigner

```{r}
m_party_history_natl <- cleaned_assets %>%
  mutate(
    previous_constituency_name = ifelse(cons_nam < 0, NA, cons_nam),
    previous_constituency_type = ifelse(cons_type == "", NA, cons_type),
    previous_constituency_year = recode(
      ifelse(year %in% c(-99, 1000, 8888), NA, year),
      `2048` = 2018, 
      `2103` = 2013
    ),
    dual_nationality = recode(
      ifelse(name_country %in% c("", "-99"), NA, name_country),
      `Canadia` = "Canada",
      `Dubai` = "UAE",
      `Engaland` = "United Kingdom",
      `Saudia` = "Saudi Arabia",
      `Uae` = "UAE",
      `Uk` = "United Kingdom",
      `Usa` = "USA",
      `Karadic Pakistan` = "Pakistan"
    ),
    contact_num = ifelse(
      contact_num %in% c("88888888888", "99999999699", "99999999999"),
      NA,
      contact_num
    )
  ) %>%
  mutate_at(
    vars(starts_with("contri_")), 
    funs(ifelse(. %in% c(-99, .96, .99, 99) | . > 10e10, NA, .)) # could be CNIC
  ) %>%
  select(key, starts_with("previous_constituency"), dual_nationality, starts_with("contri_"), contact_num)
head(m_party_history_natl)
table(m_party_history_natl$contri_from_party)
table(m_party_history_natl$contri_to_party)

```
The renaming is necessary so as to prevent confusion with the cons_name and type of current election.


#### FY Assets

```{r}
m_fy_assets <- cleaned_assets %>%
  mutate_at(
    vars(current_fy_net_assets,past_fy_net_assets),
    funs(ifelse(. %in% c(-999,-9,-99,.96,.99,99), NA, .))
  ) %>%
  mutate(fy_net_assets_change = current_fy_net_assets - past_fy_net_assets) %>%
  rename(
    fy_net_assets_current = current_fy_net_assets,
    fy_net_assets_past = past_fy_net_assets
  ) %>%
  select(key, starts_with("fy_net_assets_"))
head(m_fy_assets)
         #change_error = fy_net_assets_change != change_assets)

  # filter(!change_error)%>%
  # select(current_fy_net_assets, past_fy_net_assets, change_assets,fy_net_change,change_error)
  # 


```
A brief look tells us that the existing variable documenting called change_assets is wrong, so the new constructed **fy_net_assets_change** should be used as the accurate measure of net change. I would delete change_assets, but not doing so for now in case you want to keep it.


### Part 4: The final dataset

```{r}
out_data <- reduce(
  list(
    select(cleaned_assets, key, uid, cnic, enum_name, constituency_code, candidate_name, father_name) %>%
      mutate(cnic = as.character(cnic)),
    m_demographics,
    m_party_history_natl,
    m_crimes,
    m_agriculture,
    m_agri_total,
    m_income_taxes_trips,
    m_fy_assets,
    m_prop_capital_wide,
    m_prop_types,
    m_prop_capital_totals,
    m_invest_totals,
    m_other_capital,
    m_jewelry,
    m_motor_cost,
    m_car_totals,
    m_cash_liabilities
  ),
  left_join,
  by = "key"
)
write_csv(out_data, "data/pk18_candidate_assets_master.csv")
```

Still to clean:

1. Categorize **educ**, **occup**.
2. Waiting on AT for **motor_cost** and **motor_number** which currently have no observations.
3. Value for agri land holding?
