---
title: "Asset Check Report Final"
author: "Ibrahim Khan"
date: "8/25/2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(estimatr)
library(haven)
library(readxl)
#loading final data

setwd("C:/Users/Ibrahim Amir/Dropbox/Pakistan_Assets")

final_assets <- read_dta("data/Asset Form Data_Luke.dta")%>%
  mutate_at(vars(uid,cnic), funs(as.character))
#write.csv(final_assets, "data/Asset Form Data_Luke.csv")

check_data <- read_csv("data/Asset Form Data_Luke.csv", na = c("", "-"))
scrutiny_list <- read_csv("data/candidate_scrutiny_list.csv")%>%
  mutate(cnic=as.character(candidate_CNIC_ECP))
final_cand_uids <- read_excel("data/candidate_uids_complete.xls")


#1: Check for entry errors as we previously did
errs <- final_assets %>%
  mutate_at( #check for numeric entries are all numeric
    vars(starts_with("im_prop_pak"),bus_cap_wpk_num, bus_cap_wpk_count, 
         starts_with("bus_cap_wpk_am"), bus_cap_opk_num, bus_cap_opk_count, 
         starts_with("bus_cap_opk_am"), bank_drafts:motor_cost, motor_g_count:liabilities,
         dependents, num_criminal, crimes_count, ntn,year_income:income_total, starts_with("income_total"),
         starts_with("tax_paid"), intern_trips_cost:passport_for, current_fy_net_assets:contact_num,
         -year_income, -year_agri_income, -passport_for, -elected_before, -ntn, -starts_with("im_prop_pak_t_"),-starts_with("im_prop_pak_a_"),-starts_with("unit_agri"), -cons_type
         ),
    funs(num_val_error = . != "" & !is.na(.) & is.na(as.numeric(.)) )
  ) %>%
  mutate(CNIC_val_error = (nchar(cnic)!=13), #I also want those for which CNIC is blank or -99
         #phone_val_error = !(nchar(contact_num)==10 | contact_num==99999999999 | contact_num=="" | is.na(contact_num)),
         uid_val_error = (nchar(uid)>5 | (uid<=0 & uid!=-9999) | is.na(as.numeric(uid)) | uid=="" ), #flags blanks. Doesn't flag -9999
         cnic_missing = !(cnic %in% scrutiny_list$cnic) & cnic!=9999999999999
         ) %>%
  filter_at(
    vars(ends_with("val_error")),
    any_vars(.)
  )
#write.csv(errs, file = "data/flagged_entries_final.csv", row.names = FALSE)

# CHECKING FOR ERRORS IN CNIC ENTRIES

missing_cnics_raw <- errs%>%
  filter(cnic_missing)%>%
  mutate(seat_id = paste0(type_seat, "-", const_number)) %>%
  select(seat_id, candidate_name, uid, cnic, cnic_missing)

#write.csv(missing_cnics_raw, file = "data/missing_cnics.csv", row.names = FALSE)

#missing_cnics_categorized <- read_excel("data/missing_cnics_categorized.xlsx")%>%
#  mutate(cnic=as.character(cnic), correct_cnic=as.character(correct_cnic), uid=as.character(uid))

```


#### 1. CNIC Value Errors
A brief look at the cnic entries tells us that a of the total 3482 flagged errors, 3285 have errors with their CNIC entry. This is because the CNIC values have been stored by adding lagging zeros instead of the whole CNIC. E.g 3.45e+12 becomes 3450000000 for these errors. Do note that the error may occur in the importing of data into R, but this is unlikely because this only happens for these values, the likely explanation is that this is how they are stored in the final dta file as well. If you have Stata 14, this should be confirmed.

```{r, echo=FALSE}
errs%>% 
  group_by(CNIC_val_error, cnic_missing)%>%
  summarize(count=n())

# errs%>%
#   filter(CNIC_val_error)%>%
#   mutate(length_cnic=nchar(cnic))%>%
#   #select(cons_type,cons_nam, candidate_name, cnic, length_cnic)
#   {table(.$length_cnic)}
  
```

#### 2. Missing UIDs

Of the total 17398 observations, we only have uids for 8714 candidates. The UID is missing (-9999) for 8684 candidates. Since we want to match by names with the candidate result list, this creates a major hurdle. 8709 are matched to the final candidates list, with only 5 unmatched of those not missing (of which two have an entry error). 

```{r, echo=FALSE}

final_assets%>%
  mutate(
    uid_missing=case_when(
    (!(as.numeric(uid) %in% as.numeric(final_cand_uids$uid)) & uid!=-9999) ~ "Not Matched",
    (as.numeric(uid) %in% as.numeric(final_cand_uids$uid) & uid!=-9999) ~ "Matched",
    uid==-9999 ~ "Missing")
  )%>%
  # filter(uid_missing=="Not Matched")%>%
  # select(cons_type, cons_nam, candidate_name, uid)
  {table(.$uid_missing)}

#the reason I do as.numeric here is that the importing from dta loses the leading zeros in uid whereas it doesn't for the candidate final list. To ensure they are correctly matched, I convert both to a number. This shouldn't cause any problems in matching otherwise.
           
```

#### 3. Assets (Immovable)

While there is an added variable that is supposedly the sum of all im_prop value variables, it seems they haven't controlled for when one of the values in the sum is NA. So just to check how many total immovable property value sums we actually have in our dataset:
```{r echo=FALSE}
#to see h
#step 1: replace all -99 and NA with 0 in imp_prop_pak_p* (1-23)

final_assets%>%
  mutate_at(vars(starts_with("im_prop_pak_p_")), funs(recode(., `-99`=0,`-96`=0,`-9`=0)))%>% #there were 5 for which entries were incorrect
  mutate_at(vars(starts_with("im_prop_pak_p_")), funs(replace(., is.na(.),0)))%>%
  mutate(im_prop_value_total=im_prop_pak_p_1+
           im_prop_pak_p_2+
           im_prop_pak_p_3+
           im_prop_pak_p_4+
           im_prop_pak_p_5+
           im_prop_pak_p_6+
           im_prop_pak_p_7+
           im_prop_pak_p_8+
           im_prop_pak_p_9+
           im_prop_pak_p_10+
           im_prop_pak_p_11+
           im_prop_pak_p_12+
           im_prop_pak_p_13+
           im_prop_pak_p_14+
           im_prop_pak_p_15+
           im_prop_pak_p_16+
           im_prop_pak_p_17+
           im_prop_pak_p_18+
           im_prop_pak_p_19+
           im_prop_pak_p_20+
           im_prop_pak_p_21+
           im_prop_pak_p_22+
           im_prop_pak_p_23,
         im_prop_missing=(im_prop_value_total<=0)
         )%>%
  # select(starts_with("im_prop_pak_p_"), im_prop_value_total, im_prop_missing)%>%
  # filter(im_prop_value_total==0)%>%
  # select(im_prop_pak_p_1:im_prop_pak_p_5, im_prop_value_total, im_prop_missing)
  mutate_at(vars(starts_with("im_prop_pako_p_")), funs(recode(., `-99`=0,`-96`=0,`-9`=0)))%>% #there were 5 for which entries were incorrect
  mutate_at(vars(starts_with("im_prop_pako_p_")), funs(replace(., is.na(.),0)))%>%
  mutate(im_prop_opk_value_total=im_prop_pako_p_1+
           im_prop_pako_p_2+
           im_prop_pako_p_3+
           im_prop_pako_p_4+
           im_prop_pako_p_5+
           im_prop_pako_p_6+
           im_prop_pako_p_7,
         im_prop_opk_missing=(im_prop_opk_value_total<=0)
         )%>%
  # select(starts_with("im_prop_pak_p_"), im_prop_value_total, im_prop_missing)%>%
  # filter(im_prop_value_total==0)%>%
  # select(im_prop_pak_p_1:im_prop_pak_p_5, im_prop_value_total, im_prop_missing)
  {table(.$im_prop_missing, .$im_prop_opk_missing)}
```

It appears there are 6797 candidates who have declared no immovable assets in Pakistan. Similarly, only 195 candidates have declared immovable asset ownership outside Pakistan. 

There are 6765 candidates in total who have declared zero immovable assets (both outside and inside Pakistan).

#### Jewellery, Cash and others

In addition to immovable asset values and details, other measures of wealth we have are:
1. Business Capital Ownership within and outside Pakistan
2. Investments in varying forms (stocks, loans, mortages)
3. Total value of owned motor cars (the motor car number and count ALL NA majorly)
```{r echo=FALSE}
table(final_assets$motor_g_count, useNA="always")
```
4. Jewellery: 7678 candidates have reported the value of jewellery owned, and of those for which value is not available, we have the weights of 2197 as shown in the table below.
```{r echo=FALSE}

final_assets%>%
  mutate(jewel_val_av=case_when(
    (jewel_cost>0) ~ "Value Available",
    (jewel_cost==0) ~ "Zero",
    (jewel_cost==-99| jewel_cost=="") ~ "Value Not Available"
  ))%>%
   mutate(jewel_tola_av=case_when(
    (jewel_tolas>0) ~ "Weight Available",
    (jewel_tolas==0) ~ "Zero",
    (jewel_tolas==-99 | jewel_tolas=="") ~ "Weight Not Available"
  ))%>%
  {table(.$jewel_val_av, .$jewel_tola_av, useNA = "always")}
```
5. Cash in hand and at bank are estimates of the total funds in cash available to any candidate. This may be important both in that we expect this to be the main pool from which expenditure for the campaign may take place, given it is not easy to sale off immovable property to fund an election at short notice (assuming the records are up to date till submission of nomination forms). We have total cash details available for 12235 candidates, which is a good sign.
```{r echo=FALSE}

final_assets%>%
  mutate_at(vars(cash_cost, cash_bank_cost), funs(recode(., `-99`=0)))%>%
  mutate(total_cash=cash_cost+cash_bank_cost)%>%
  # filter_at(.,vars(cash_cost, cash_bank_cost),any_vars(.<0))%>%
  # select(cash_cost,cash_bank_cost  )
  mutate(total_cash_available=total_cash>0)%>%
{table(.$total_cash_available)}


```
6. Agricultural and total income as declared in affidavits.
7. Size of Agricultural land holdings. This is varying since some have reported in Acres, others in Kanals. We have such details for 1304 candidates
```{r echo=FALSE}
final_assets%>%
  mutate(agriland_holding_details=(agri_land_holding>0|agri_land_holding1>0|agri_land_holding2>0))%>%
  {table(.$agriland_holding_details, useNA = "always")}

```
8. Current fy and past fy net assets: we have reported values for both of these for 10235 candidates
```{r echo=FALSE}
final_assets%>%
  mutate(fy_assets_av=current_fy_net_assets>0 | past_fy_net_assets>0)%>%
  {table(.$fy_assets_av)}

```
#### Steps to consider going forward
* First priority should be to resolve missing and unmatched uids, as these form the basis for matching by name accurately with the election results.
* Next is to resolve the CNIC lagging zero errors that I experienced today, which will then allow for a clear picture of how many missing or erroneous CNICs we have in the data
* Occupation and Education variables need to be cleaned and categorized
* It would be useful to group asset types in a few broad categories such as: 
  + Immovable Property Value Total 
  + Agricultural Land Ownership Value
  + Agricultural Income
  + Movable Property Value Total (includes cash, automobile, jewellery)
* To evaluate land at current prices, it might be useful to look at Land Revenue Annual _Mossat_ _Bay_ (reports land price value at mouza level)
* For jewellery, I am unsure since the weight of jewellery does not capture type (silver, gold) whose prices may differ.  
